\section{Introduction}
\frame
{
\frametitle{Introduction}
\begin{itemize}
	\item Very important topic in the Robotic area.
	\begin{itemize}
		\item Main idea: paths, obstacles.
		\item Optimal path: time, distance, energy.
	\end{itemize}
	\item Problem approach.
	\begin{itemize}
		\item C-Space method
		\item Potential field method
		\item Neural networks
		\item Genetic algorithms
	\end{itemize}
\end{itemize}
}

\frame
{
\frametitle{Introduction}
\begin{itemize}
	\item Main difficulties are computational complexity, local optimization and adaptability.
	\item Previous work
	\begin{itemize}
		\item GA variations.
	\end{itemize}
\end{itemize}
}
\frame
{
\frametitle{Introduction}
\begin{itemize}
	\item Why not Ga?
	\begin{enumerate}
		\item Individual encoding of robot path is illogical, evolution efficiency is low, and illegal individuals are always produced in the process of evolution.
		\item Fitness function of individual is not designed exactly, so that quality of paths belonging to inhomogeneity is difficult to measure
		\item Genetic operators is not devised logically, the effect of evolution is not evidence.
		\item Field knowledge is not used in the mobile robot path planning, the efficiency of evolution is low.
	\end{enumerate}
\end{itemize}
}

\frame
{
\frametitle{Introduction}
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{itemize}
	\item AIS features
	\begin{itemize}
		\item Diversity
		\item Dynamic
		\item Parallel management
		\item Self-organization
		\item Self-adaptation
	\end{itemize}
\end{itemize}
\end{column}

\begin{column}{0.5\textwidth}
\begin{itemize}
	\item Where?
	\begin{itemize}
		\item Data Mining
		\item Network security
		\item Pattern recognition
		\item Learning
		\item Optimization
	\end{itemize}
\end{itemize}
\end{column}
\end{columns}
}


